---
title: "Project_2"
author: "Regis Ouedraogo"
date: '2022-11-03'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
PROJECT:

2. Use the Stock returns from the 3 stocks:
Estimate the Beta’s for each stock.

Estimate the Expected Return for each stock. Use formulas in Part E

3. Build a Linear Model for the Three-Factor-Model , using the indices from website

Estimate the Expected Return for each stock, using the Fama-French data. Use formulas inf Part F

Compare with the previous results in (2). 


(1) Explore stock prices- returns


```{r}
library(quantmod)

start<- as.Date("2020-11-04")
end<- as.Date("2022-11-03")
btc <-getSymbols("BTC",from=start, to=end, auto.assign=F)
wmt <-getSymbols("WMT",from=start, to=end, auto.assign=F)
atom <-getSymbols("ATOM",from=start, to=end, auto.assign=F)
returns.BTC <- dailyReturn(btc$BTC.Close)
returns.WMT <- dailyReturn(wmt$WMT.Close)
returns.ATOM <- dailyReturn(atom$ATOM.Close)
```


## combine into an xts-object of all returns

```{r}
returns <-cbind(returns.BTC, returns.WMT ,returns.ATOM)
colnames(returns)<- c("BTC.ret", "WMT.ret", "ATOM.ret")
head(returns)
```


## Returns of BTC, WMT Inspection of returns
```{r}
hist(returns.BTC, probability = TRUE, main="btc returns")
# calculate skewness in r
#install.packages("moments")
library(moments)
skewness(returns.BTC)
kurtosis(returns.BTC)

```
```{r}
#install.packages("e1071")
 library(e1071)     
log.ret_Btc <- log(1+returns.BTC)
hist(log.ret_Btc)
skewness(log.ret_Btc)
```

```{r}
log.ret_ATOM <- log(1+returns.ATOM)
hist(log.ret_ATOM)
skewness(log.ret_ATOM)
```

```{r}
log.ret_wmt <- log(1+returns.WMT)
hist(log.ret_wmt)
skewness(log.ret_wmt)
```
```{r}
mu.d <- mean(log.ret_ATOM)
median.d <- median(log.ret_ATOM)
sigma.d <- sd(log.ret_ATOM)

cat(" ATOM Mean:", round(mu.d, 6), "\n",
    "ATOM Median:", round(median.d, 6), "\n",
    "ATOM Standard Deviation:", round(sigma.d, 6))
```


```{r}
mu.d <- mean(log.ret_Btc)
median.d <- median(log.ret_Btc)
sigma.d <- sd(log.ret_Btc)

cat(" BTC Mean:", round(mu.d, 6), "\n",
    "BTC Median:", round(median.d, 6), "\n",
    "BTC Standard Deviation:", round(sigma.d, 6))
```



```{r}
mu.d <- mean(log.ret_wmt)
median.d <- median(log.ret_wmt)
sigma.d <- sd(log.ret_wmt)

cat(" WMT Mean:", round(mu.d, 6), "\n",
    "WMT Median:", round(median.d, 6), "\n",
    "WMT Standard Deviation:", round(sigma.d, 6))
```




(2) Efficiency Frontier
### Efficient frontier
```{r}

wt1 <- seq(-2,2, by=.1)
wt2 <-seq(-2,2, by=.1)
wt3 <- 1 -wt1-wt2
wts<- cbind(wt1,wt2,wt3)
mean.returns <- apply(returns, 2, mean)
covariance <- 252*cov(returns) # annualized variance/covariance
covariance
```

```{r}
## calculate portfolio return and risk
port.return <- c()
for (i in 1:41){
port.return[i] <- wts[i, ] %*% mean.returns
}
head(port.return)
## calculate portfolio risk
port.variance <-c()
for (i in 1:41) {
 port.variance[i] <- t(wts[i , ]) %*% covariance %*% wts[i , ]

}
head(port.variance)
port.risk <-sqrt(port.variance) ## risk is square root of variance
head(port.risk)
plot(port.risk, port.return, type="b", main="Efficient Frontier,BTC+WMT+ATOM")
```


(3) Risk-free rate and Market Portfolio return

```{r}

rf<-getSymbols("DGS1",src="FRED" ,auto.assign = F)
dim(rf)

#rf1 <- rf[ date >= "2021-11-04" & date<="2022-11-03", ]
rf <- na.omit(rf)
riskfree <-mean(rf)/100
riskfree

```


## Market portfolio

```{r}

benchmark<-getSymbols.yahoo("^GSPC", from=start, to=end, periodicity = "daily",auto.assign=F)[ ,4]
bench.returns <- dailyReturn(benchmark) 
```

(5) Study of individual stock return: beta

```{r}
## beta for BTC
beta.BTC <- cov(bench.returns, returns.BTC)/var(bench.returns)
beta.BTC

## beta for USDC
beta.WMT <- cov(bench.returns, returns.WMT)/var(bench.returns)
beta.WMT

## beta for ATOM
beta.ATOM<- cov(bench.returns, returns.ATOM)/var(bench.returns)
beta.ATOM
```

3 -Factor Pricing Model: 

```{r}
# use read.table for text file
ff_data = read.csv("F-F_Research_Data_Factors_daily.CSV", skip = 3)
ff_data = na.omit(ff_data)  #remove missing values

head(ff_data)  #date is missing column names
```


```{r}
colnames(ff_data)[1] = "Date"
# convert dates in R date format
ff_data$Date = as.Date(strptime(ff_data$Date, format = "%Y%m%d"))
head(ff_data)
```


```{r}
d_wmt = getSymbols("WMT", from = "2020-11-03", to = "2022-11-03", auto.assign = F)
# select closing prices and covert to log returns

wmt = d_wmt$WMT.Close
wmt_ret = dailyReturn(wmt, type = "log")

# convert to data frame
wmt_ret2 = fortify.zoo(wmt_ret)  #Dates column will be named Index

# rename
colnames(wmt_ret2) = c("Date", "WMT")

# use merge (can use left_join from dplyr as well) to combine the
# stock returns and factor data

data_ffex = merge(wmt_ret2, ff_data, by = "Date")

# create another column with WMT-RF

data_ffex$WMT.Rf = data_ffex$WMT - data_ffex$RF

ff_lreg = lm(WMT.Rf ~ Mkt.RF, data = data_ffex)
summary(ff_lreg)
```

```{r}

d_btc = getSymbols("BTC", from = "2020-11-03", to = "2022-11-03", auto.assign = F)
# select closing prices and covert to log returns

btc = d_btc$BTC.Close
btc_ret = dailyReturn(btc, type = "log")

# convert to data frame
btc_ret2 = fortify.zoo(btc_ret)  #Dates column will be named Index

# rename
colnames(btc_ret2) = c("Date", "BTC")

# use merge (can use left_join from dplyr as well) to combine the
# stock returns and factor data

data_ffex = merge(btc_ret2, ff_data, by = "Date")

# create another column with BTC-RF

data_ffex$BTC.Rf = data_ffex$BTC - data_ffex$RF

ff_lreg = lm(BTC.Rf ~ Mkt.RF , data = data_ffex)
summary(ff_lreg)
```

```{r}

d_atom = getSymbols("ATOM", from = "2020-11-03", to = "2022-11-03", auto.assign = F)
# select closing prices and covert to log returns

atom = d_atom$ATOM.Close
atom_ret = dailyReturn(atom, type = "log")

# convert to data frame
atom_ret2 = fortify.zoo(atom_ret)  #Dates column will be named Index

# rename
colnames(atom_ret2) = c("Date", "ATOM")

# use merge (can use left_join from dplyr as well) to combine the
# stock returns and factor data

data_ffex = merge(atom_ret2, ff_data, by = "Date")

# create another column with ATOM-RF

data_ffex$ATOM.Rf = data_ffex$ATOM - data_ffex$RF

ff_lreg = lm(data_ffex$RF~ Mkt.RF + SMB + HML, data = data_ffex)
summary(ff_lreg)
```


